Background Music Will not Distract Students' Attention

### 2021-04-24 Output/paper/paper.Rmd
update

---
title: "Background Music Will not Distract Students' Attention"
author: "Hong Pan"
date: "`r format(Sys.time(), '%B %d %Y')`"
output:
  bookdown::pdf_document2:
    latex_engine: xelatex
    toc: yes

abstract: "Music has gradually become an essential part of our lives, and it has become a common trend for most students to choose to listen to music while studying. This paper examines whether the background music affects students' attention level by conducting a within-subjects experiment to compare the time of finishing the Trail Making Test with and without music. From the liner mixed mode, the result shows that background music does not significantly impact attention level. Apart from that, male students tend to be more easily distracted by the background music. \\par
 \\textbf{Keywords:} background music, attention, trail making test, executive functioning skills"

@@

The within-subjects experiment is conducted by randomly selected students from one specific school, and each participant needs to complete two rounds of tests, with and without music.  The dataset created by Arriken Worsley[@dataset] records the time of accomplishing the test, gender of the student, music favourability, and the order of test which is starting with the music or without the music. The descriptive analysis results show that students performed better without music. In addition, whatever the order of the test, the second round will be faster on average. Furthermore, background music has the biggest influence on male's executive functioning skills. Because the dataset is longitudinal, the linear mixed model is applied to do the statistical analysis. The result from the model illustrates that the students’ attention level is not significantly impacted by listening to the music. In this study, the practice effect^[People improve their scores simply by taking the same test multiple times. (Kendra Cherry,2019)]  may exist since the students need to do the test twice continuously.

@@

# Data
The data used to investigate whether background music will effect students' attention level. The data analyzed through R Statistical Programming Language[@citeR]. The Tidyverse package[@cite_tidyverse] used for data processing, kableExtra package[@cite_kableExtra] is applied to generate tables, ggplot2[@cite_ggplot2] is used to draw diagrams, here[@cite_here] used for import dataset and nlme[@cite_nlme] utilized to create model. The performance pacakge[@cite_performance] and lattice package[@cite_lattice] are used to draw diagram help to check the model assumptions. The package stargazer[@cite_stargazer] is used to visualize the table.

## Participants
The experiment was conducted in a high school in 2020, and the sample of the study was comprised of 47 students between 13 and 17 years old randomly chosen from the school. Both male and female students participated in the research on whether background music affects people's attention. The pie chart shown in Figure \@ref(fig:gender) illustrates that 51% are female, 47% are male, and the rest 2% are transexual.

@@

### Intervention
The purpose of the experiment is to examine the background music effects on students' attention level. The experimental design plan randomly selects some students from a school, completes the Trail Making Test with and without background music, and records the completion time. In this experiment, the intervention is the existence of background music. This experiment wants to determine whether the background music will affect the concentration level of students by studying whether the time for students to complete the test with background music is longer than the time for completing the test without background music. If the result is yes, it means that music will affect the student's attention to a certain extent; otherwise, it will not. The experiment can help the target audience have some basic understanding of whether music has an impact on attention and can make the right decision whether to listen to music in future studies or work to avoid inefficiency.

@@

The 47 students chosen randomly from the school will be randomly separated into two groups to start the Trail Making Test in a different order. 27 students started the experiment in a quiet environment, and the remaining 20 students started with background music. The Trail Making Test utilized during the experiment are shown in figure 2 and 3 in the appendix. Each test contains 23 randomly distributed dots, including 12 numeric points from 1 to 12 and 11 letter points from A to K. Participants must start connecting from 1 and connect these points to the final point in alternating ascending order, such as 1, A, 2, B, 2, C, etc. During the process, the line should not cross over, making a "trail". The background music, the intervention,  while playing during the experiment will be the song Panda by Desiigener because, during the experiment period, it was at the top of the billboard and was the most popular music.

The experiment is conducted by students in the form of a class. Students selected to the same group will start the test uniformly, and a timer is placed in front of each student to record the completion time. In order to counteract the learning effect gained from the first test to the second one to some extent, changing the order of starting the experiment was applied. The students in the first group will start the Trail Making Test without background music, then will do another test while playing the background music, Panda. The second group of students will start to do the test with background music and do the second test in silence for control. After each round, the time for accomplishing the test will be recorded by seconds. Meanwhile, when participants finish all the two tests, they will be required to fill in an anonymous survey shown in the appendix that will ask for feedback, gender, and personal enjoyment of the song played, on a scale from one to five.

@@

The **Id** represents a student, and a number represents a student. **Test_Type** illustrates whether the students finished the test with background music or without, the control group or the treatment group. **Time_Sec** shows how many seconds does the student to accomplish the Trail Making Test. The column, **Gender**, shows the gender of the student. **Rating** indicates the student's preference for background music. After completing the experiment, students need to fill out a questionnaire anonymously, including rating background music from 1 to 5. The higher the score, the more they like the background music. The `Feedback` column shows the students' feelings and evaluations of the entire experiment. **Change** shows test 2 compares with test 1, by what percentage increase or decrease the time. **Order** records the order of the test, which helps to illustrate whether the test is the first or second round.

## Descriptvie Analysis
### Gender distribution
```{r gender,fig.cap = "Gender ratio chart",echo=FALSE}
gender_ratio<-data.frame(table(dataset$Gender))

@@

### Mean time by test type
```{r table1,fig.cap='Average time to complete a test with and without background music', echo=FALSE}

@@

### Average time of completing a test by type and order

```{r order, fig.cap="Average time of completing a test by type and order",echo=FALSE,warning=FALSE,message=FALSE}
#remove package plyr for using group_by function
detach(package:plyr)
dataset %>% 
  group_by(order, Test_Type) %>% summarize("Average Time to Complete a Test" = round(mean(Time_Sec),2),'Standard Deviation'=round(sd(Time_Sec),2))%>%
kbl(caption = 'Average time of completing a test by type and order',
      align = "cccc") %>%
  kable_styling(latex_options = "hold_position")

@@

Since the experiment is a within-subject experimental design, each student is both in a control group and a treatment group. In order to study whether the practice effect exists, Table \@ref(tab:order) shows that in addition to studying the average time for students to complete the test in each experiment condition, the factor of the order of completing the test is also added.  Overall, whether the students completed the first round of the test with background music or first completed the test in a quiet environment, the average completion time of the second round was shorter than that of the first round. The Table \@ref(tab:order) shows that when students' first round is added intervention, the average time to complete the test is around 52.56 seconds(SD= 12.14). The second round, which is without background music, takes around 40.56 seconds(SD= 15.52) to accomplish the test. For the students who finish the test without background music in the first round, the average time to complete the test is 49.52 seconds(SD= 12.06). When added intervention, the background music, to the second round, the average time for them to complete the test not only did not increase, but it decreased by one second, about 39.95 seconds(SD= 10.18).

### Average time for different genders to complete the test by test type
```{r gendertime, fig.cap="Average time for different genders to complete the test by test type",echo=FALSE,warning=FALSE,message=FALSE}
d1 <- dataset %>% 
        group_by(Gender,Test_Type) %>% 
        summarise(mean_time = mean(Time_Sec))

ggplot(d1, aes(x =Gender , y = mean_time,fill=Gender)) +
  geom_bar(stat = "identity",width = 0.8)+
  facet_wrap(~Test_Type)+
  ylab("Mean time")+
  ggtitle("Average time to complete the test by gender and test type")+
  theme_minimal()+
  theme(plot.title = element_text(size=13))

@@

The paper[@female] illustrates females are good at concentration and not easily being distracted compared with males. In order to study whether background music will affect students’ attention levels differently due to different genders, Figure \@ref(fig:gendertime) is drawn. Overall, the conclusion from the graph goes along with the conclusion the Bruce Goldman[@female] made, which is females are less affected by the intervention, while males' attention levels are easily affected. Background music increased the average time for female and transexual students to complete the test by about one second. In contrast, background music influences male students' average time to complete the test increased by 5 seconds. And whether with or without background music, the average completion time for men is the longest, while the average time for transexuals is the shortest.

```{r linechart, fig.cap="Music favorability and average time to complete the test",echo=FALSE,warning=FALSE}
d2 <- dataset %>% 
        group_by(Rating)%>% 
        summarise(mean_time = mean(Time_Sec))

overall_mean_time<-mean(dataset$Time_Sec)

ggplot(d2,aes(x=Rating,y=mean_time))+
  geom_line(color='blue')+
  scale_x_continuous(breaks = seq(1,5,0.5),limits = c(1,5))+
  scale_y_continuous(breaks = seq(0,50,5),limits = c(0,50))+
  geom_hline(yintercept = overall_mean_time,
             color = "darkred",
             linetype = "dashed")+
  geom_text(aes(Rating[1], overall_mean_time , label = "Mean"), vjust= 2)+
  ggtitle("Favorability of music and average time to complete the test")

```
The line chart shown in Figure \@ref(fig:linechart) is used to visualize the relationship between the degree of enjoyment of music from students and their attention levels. The blue line indicates the average time to complete the test at each rating level, and the brown dash line represents the total average time for accomplishing the test. As we can see from the chart, when the rating is approximately less than 3, the average time for students to complete the test is all greater than the overall average. When the rating is greater than 3, the average time for all students is significantly less than the overall average except for level 4.0. According to the findings in Figure \@ref(fig:linechart), when students listen to songs they don’t like while studying or doing other things that require concentration, their attention level is easily affected.

@@

The analysis in this paper will be done entirely through R[@citeR]. From Figure \@ref(fig:randomeffect) below, each line is for 2 Trail Making Test performed by each student and shows the measured completion time of each student who performed the test under different order conditions. As clearly illustrated,  whether there is background music or no background music first, different individuals will have different levels of initial attention level, which suggests the existence of the random effects, specifically random intercepts. In addition, the slope for each line is different, which imply that random slope also exist. So, the linear mixed model is applicable. It quantified how background music played in the background could impact the students' attention level compared to the quiet background.

@@

### Random Effects
Three null models with different random effects terms will be set up, and the ANOVA function will be applied to compare the models to find the best fitting random effects structure by comparing their p-value to see whether fit has improved with additional items.

The three different random effects term are as followed:
*(1| Id): Random intercepts and slopes for each Id.
*(1 + Test_Type |Id) = The effect of the background music will vary between each student Id. Random intercepts for test type, random slopes for students influenced by test type.
* (1 + Test_Type * order | Id) = Each student Id can have their intercept, random slopes influenced by Test Type and order, and their interaction between Test Type and order.

### Fixed Effects
After finding the best-fitting random effect term, ANOVA will be applied to select the significant variables and compare different models. The model for the study starts with only focused variable, test type. Then, other variables will be included in the model one at a time. From the ANOVA output, if the p-value were smaller than 0.1, the variable would be added to the final model. In the process of determining the best model, ANOVA will be applied and the smaller AIC^[AIC(Akaike information criterion) is a mathematical method for evaluating how well a model fits the data it was generated from. AIC is used to compare different possible models and determine which one is the best fit for the data[@AIC.] suggests the better model.

@@

Figure \@ref(fig:a1) helps to check the assumption of the variance of the residuals is equal across groups. From the chart, there seems to be an evenly spread around the central line and no patterns evident, which means the assumption of homogeneity of variance being satisfied.

```{r a1, fig.cap="The variance of the residuals is equal across groups",echo=FALSE,warning=FALSE,message=FALSE}
model<-lmer(Time_Sec~ 1+Test_Type+order+Rating+Gender+(1|Id),data=dataset,REML=FALSE)

@@

QQ plots(Figure \@ref(fig:a2)) can provide an estimation of where the standardized residuals lie with respect to normal quantiles. Strong deviation from the provided line indicates that the residuals themselves are not normally distributed. From Figure \@ref(fig:a2), there is some deviation from eh expected normal line towards the two-side tails, but overall all the line looks straight and therefore pretty normal and suggests that the assumption is not violated.

```{r a2, fig.cap="The residuals of the model are normally distributed",echo=FALSE,warning=FALSE,message=FALSE}
library(lattice)
qqmath(model)
```

Variance inflation factor (VIF) is a measure of the amount of multicollinearity, which means one predictor variable can be linearly predicted from the others with a substantial degree of accuracy[@multicollinearity]. The bar chart in Figure \@ref(fig:a3) illustrates that all the independent variables in the model have a VIF value less than 2.5, which means there are low, and even no multicollinearity exists.
```{r a3, fig.cap="multicollinearity",echo=FALSE,warning=FALSE,message=FALSE}
library(performance)

@@

## Full Model Result
After finding the best-fit random effect term, the predictor variables will be added to the model one by one. Model 1 in the table only includes the most important variable, Test_Type. The result in the table(Table \@ref(tab:r2)) shows that the coefficient of Test_Type is -2.936 with a 90% confidence level is -8.064 to 2.192,  which illustrates that the average time for completing the Trail Making Test with or without background music is not significantly different between groups. Then, the variable order was added to model 2. The result from the Table \@ref(tab:r2) shows that the coefficient for the variable order is -10.65 and the 90% confidence interval is  -14.848 to -6.452, which does not cover value 0, suggesting that the average time to complete the test in order 2 is 10.65 seconds faster than the order 1, holding other variables constant. Meanwhile, for model 3, the interaction between test type and order being considered for testing whether the effect of the order variable depending on the level of test type. The output from model 3 shows that the interaction term is not significant, p-value larger than 0.1 and the 90% confidence interval cover value 0. Furthermore, variable Rating was added to model 4 and showed not significantly related to completing the test. Finally, the same logic applied to model 5, which plus variable Gender and illustrate that the different Gender would not be a factor to influence student's time of accomplishing the test.

In order to find out the best-fit model for the data, ANOVA and AIC were applied to compare models. In Table \@ref(tab:r2), there is an AIC value in each model. The smaller the AIC value, the better the model. From Model 1 to Model 5, their AIC values are 760.54, 742.68, 744.21, 746.02, and 747.68 respectively. Among them, the AIC value of Model 2 is the smallest. Therefore, it is deduced that Model 2 should be the best model among the five models.To further prove that model two is the best model among the five, ANOVA is used to compare the five models. In Table \@ref(tab:r3), analyze which model is the best by looking at the p-value. When comparing model 1 and model 2, the p-value is much smaller than 0.01, which shows that model two is significantly better than model one, so model two is the best at this time. When comparing model two and model three, the p-value is 0.497, which is greater than 0.1, so adding predictor variables does not increase the fittness of the model. The same logic applies to the comparison between Model 3 and Model 4 and Model 4 and Model 5. In conclusion, through ANOVA's analysis, the conclusion is that Model 2 is still the best.

```{r r2, fig.cap="Model comparison results",echo=FALSE,warning=FALSE,message=FALSE,comment=NA}
library(stargazer)
m1<-lmer(Time_Sec~ 1+Test_Type+(1|Id),data=dataset,REML=FALSE)

@@

m5<-lmer(Time_Sec~ 1+Test_Type+order++Test_Type*order+Rating+Gender+(1|Id),data=dataset,REML=FALSE)

stargazer(m1,m2,m3,m4,m5, type = "text",
          title = "Linear Mixed Model Result",
          digits = 3,
          star.cutoffs = c(0.05, 0.01, 0.001),
          digit.separator = "",
           align=TRUE,
           ci=TRUE)

@@

## Model Assessment Result
Root Mean Square Error(RMSE) is used to evaluate the quality of the model. RMSE stands for the standard deviation of the residuals and it helps to tell how concentrated the data is around the line of best fit[@RMSE]. In Table \@ref(tab:r4), the RMSE value of the final model, model 2, is 0.135 which a good sign for the model and illustrates that the model have good ability to accurately predict the data. The R-square is applied to assess the model as well. R-square is a statistical measure of how close the data are to the fitted regression line[@R-square]. For the linear mixed model, R-square consisted two types, which are marginal R-square and conditional R-square. The paper will mainly focused on marginal R-square values, which provides the variance explained by only fixed effect. The marginal R-square for the final model, model 2, shown in Table \@ref(tab:r4) is 0.169, which means 16.9% of the variation in the dependent variable can be explained by the final linear mixed model.
```{r,include=FALSE}
#RMSE:
performance_rmse(m2,normalized = TRUE)

@@

# Discussion
## Bias and ethical concerns
### Ethics Statement
The experiment conducted in this paper is about learning whether background music will influence students' attention level. The intervention in the study is background music. There is no potential to harm or endanger any participant. Moreover, the designer did not collect any sensitive data. Therefore, no formal ethics approval is required.

### Practice Effect
Each participant is measured for two conditions in the within-subject design(repeated measure design). Participants learn about the type and difficulty of the question when they take the Trail Making Test for the first time, so they may become more adept simply with the question and more proficient because of the repeated test, making the second-round test result more optimistic. In addition to the students' understanding of the test questions, some participants may feel bored or have a negative attitude to repeat the same test, making the results inaccurate.

### Hawthorn Effect
During the experiment, participants know that they are part of the experiment and observed. Their speed of doing the tests and the performance will be recorded, leading to the Hawthorne effect. Hawthorne effect stands for the tendency of some people to perform better when they know they are the participants in an experiment. The existence of the Hawthorne effect may cause students to change their behavior, such as trying to complete the test as soon as possible to achieve better performance, precisely because they know they are receiving research attention. Then, the results may be biased and inaccurate.

@@

### Male are more susceptible to music interference
When comparing the average time to complete the test with and without background music for different genders, the results show that the change in female and transexual people is not obvious. After adding interference factors, the average time to complete the test increases by one second. However, the average time for males to complete the test was 45 seconds before adding the interference factor. After the interference factor was added, the average time to complete the test was 50 seconds. The background music increased the completion time for the male by 5 seconds. Therefore, in all the participants in this experiment, males are more likely to be disturbed by background music, which affects their attention level.

@@

### Each student’s initial attention level is different

. Statistical Analysis:
  1) random intercept and random slop occurs
  2) each students whatever which group they belong to have different attention level.
  3) background music is not significantly impact studnets' attention level, but order did influnce the time of completing the test.

## What is something that we learn about the world?
.

## What are some weaknesses of what was done?
. internal validity: justified by the procedures of sampling, randomization in the experiment intervention, controlling or confounders and having sufficient sample size in the model.
  1) sampling: 
  2) Randomization in intervention
  3) Controlling for confounders
  4) Sufficient sample size

.External validity: cannot be representative

## What is left to learn or how should we proceed in the future?
. add more students to do the experiments
. change the setting to different types of experiments with Stroop Test.

\newpage
# Appendix
```{r test1, echo=FALSE, fig.align='center', fig.cap="First Trail Making Test", out.width = '80%'}
knitr::include_graphics(here("Output/images/test1.png"))
```

>>>>

---
title: "Background Music Will not Distract Students' Attention"
author: "Hong Pan"
date: "`r format(Sys.time(), '%B %d %Y')`"
output: 
  bookdown::pdf_document2:
    toc: yes

abstract: "Music has gradually become an essential part of our lives, and it has become a common trend for most students to choose to listen to music while studying. This paper examines whether the background music affects students' attention level by conducting a within-subjects experiment to compare the time of finishing the Trail Making Test with and without music. From the liner mixed mode, the result shows that background music does not significantly impact attention level. Apart from that, male students tend to be more easily distracted by the background music. \\par

 \\textbf{Keywords:} background music, attention, trail making test, executive functioning skills"

@@

The within-subjects experiment is conducted by randomly selected students from one specific school, and each participant needs to complete two rounds of tests, with and without music.  The dataset created by Arriken Worsley[@dataset] records the time of accomplishing the test, gender of the student, music favourability, and the order of test which is starting with the music or without the music. The descriptive analysis results show that students performed better without music. In addition, whatever the order of the test, the second round will be faster on average. Furthermore, background music has the biggest influence on male's executive functioning skills. Because the dataset is longitudinal, the linear mixed model is applied to do the statistical analysis. The result from the model illustrates that the students’ attention level is not significantly impacted by listening to the music. The paper concludes that the background music does not significantly impact students' attention level. In this study, the practice effect^[People improve their scores simply by taking the same test multiple times. (Kendra Cherry,2019)]  may exist since the students need to do the test twice continuously.

@@

# Data
The data used in this paper analyzed through the R statistical programming language[@citeR] to investigate whether background music affects students' level of attention. The Tidyverse package[@cite_tidyverse] for data processing, the KableExtra package[@cite_kableExtra] and plyr package[@cite_plyr] for generating tables, and the ggplot2 package[@cite_ggplot2] for drawing graphs are used during the analysis process. Meanwhile, the here package[@cite_here] for importing datasets and the lme4 package[@cite_lme4] for creating models are also used. The performance package[@cite_performance], lattice package[@cite_lattice] and MuMIn package[@cite_MuMIn] are used to draw charts, check model assumptions and model validity. Finally, the stargazer package[@cite_stargazer] is applied to visualize the model result.

## Participants
The researcher experimented in 2020 at the Elizabeth Blackburn School of Science, a secondary school funded by the Melbourne government. The study sample comprised 47 students between 13 and 17 years old randomly chosen from the school. Both male and female students participated in the research on whether background music affects people's attention. Figure \@ref(fig:gender), the pie chart, illustrates that 51% are female, 47% are male, and the rest 2% are transexual.

@@

### Intervention
The purpose of the experiment is to examine whether background music affects the attention of students. The design of the experiment was to randomly select some students from the school to complete the "Trail Making Test" with and without background music and record the time of completion. For this experiment, the intervention is the presence of background music. Experiment designer Arriken Worsley wanted to determine whether background music would affect students' attention level by studying whether students took longer to complete the test with background music than without background music. If the result is that the time for the student to complete the test with background music is longer than the time without background music, it means that the background music affects the student's attention to a certain extent. Otherwise, background music will not affect students' attention. The experiment can help the target audience develop some basic understanding of whether music impacts attention and correctly decide whether to listen to music in future studies or avoid inefficiency.

@@

The 47 students chosen randomly from the school will be randomly separated into two groups to start the Trail Making Test in a different order. 27 students started the experiment in a quiet environment, and the remaining 20 students started with the existence of background music. Figure \@ref(fig:test1) and Figure \@ref(fig:test2) in the appendix show two different Trail Making Test used in different test environments during the experiment. Each test contains 23 randomly distributed dots, including 12 numeric points from 1 to 12 and 11 letter points from A to K. Participants must start connecting from 1 and connect these points to the final point in alternating ascending order, such as 1, A, 2, B, 3, C, et cetera. During the process, the line should not cross over. The background music, the intervention,  while playing during the experiment will be the song Panda by Designer because, during the experiment period, it was at the top of the billboard and was the most popular music.

The experiment was conducted in the form of a class. Students selected to the same group started the test uniformly, and a timer was placed in front of each student to record the completion time. In order to counteract the learning effect gained from the first test to the second one to some extent, changing the order of starting the experiment was applied. The students in the first group started the Trail Making Test without background music, then did another test while playing the background music, Panda. The second group of students started to do the test with background music and did the second test in silence for control. After each round, the accomplishing time was recorded in unit second. Meanwhile, when participants finished all the two tests, they were required to fill in an anonymous survey(Figure \@ref(fig:survey)) shown in the appendix that asked for feedback, gender, and personal enjoyment of the song played, on a scale from one to five.

@@

The **Id** represents a student, and a number represents a student. **Test_Type** illustrates whether the students finished the test with background music or without, which indicates the data comes from the control group or the treatment group. **Time_Sec** shows how many seconds does the student to accomplish the Trail Making Test. The column, **Gender**, shows the gender of the student. **Rating** indicates the student's preference for background music. After completing the experiment, students need to fill out a questionnaire(Figure \@ref(fig:survey) in appendix) anonymously, including rating background music from 1 to 5. The higher the score, the more they like the background music. The `Feedback` column shows the students' feelings and evaluations of the entire experiment. **Change** shows test 2 compares with test 1, by what percentage increase or decrease the time. **Order** records the order of the test, which helps to illustrate whether the test is the first or second round.

## Descriptvie Analysis
### Gender distribution

```{r gender,fig.cap = "Gender ratio chart",echo=FALSE,fig.height=5,fig.width=5}
gender_ratio<-data.frame(table(dataset$Gender))

@@

### Mean time by test type

```{r table1,fig.cap='Average time to complete a test with and without background music', echo=FALSE}

@@

### Average time of completing a test by type and order
Since the experiment is a within-subject experimental design, each student is both in a control group and a treatment group. In order to study whether the practice effect exists, Table \@ref(tab:order) shows that in addition to studying the average time for students to complete the test in each experiment condition, the factor of the order of completing the test is also added.  Overall, regardless of whether students completed the first round of the test with background music or quietly, the average completion time of the second round was shorter than the average time of the first round. Table \@ref(tab:order) shows that when students' first round is added intervention, the average time to complete the test is around 52.56 seconds(SD= 12.14). The second round, which is without background music, takes around 40.56 seconds(SD= 15.52) to accomplish the test. For the students who finish the test without background music in the first round, the average time to complete the test is 49.52 seconds(SD= 12.06). When added intervention, the background music, to the second round, the average time for them to complete the test not only did not increase, but it decreased by one second, about 39.95 seconds(SD= 10.18).

```{r order, fig.cap="Average time of completing a test by type and order",echo=FALSE,message=FALSE}
#remove package plyr for using group_by function
detach(package:plyr)
dataset %>% 
  group_by(order, Test_Type) %>% summarize("Average Time to Complete a Test" = round(mean(Time_Sec),2),'Standard Deviation'=round(sd(Time_Sec),2))%>%
kbl(caption = 'Average time of completing a test by type and order',
      align = "cccc") %>%
  kable_styling(latex_options = "hold_position")
```

### Average time for different genders to complete the test by test type

The paper[@female] written by Bruce Goldman illustrates that females are good at concentration and not easily being distracted compared with males. In order to study whether background music will affect students' attention levels differently due to different genders, Figure \@ref(fig:gendertime) is drawn. Overall, the conclusion from the graph goes along with the conclusion Bruce Goldman made[@female]: females are less affected by the intervention. At the same time, males' attention levels are easily affected. The descriptive analysis result shows that background music increased the average time for female and transexual students to complete the test by about one second. In contrast, background music influences male students' average time to complete the test increased by 5 seconds. Moreover, whether with or without background music, the average completion time for men is the longest, while the average time for transexuals is the shortest.
```{r gendertime, fig.cap="Average time for different genders to complete the test by test type",echo=FALSE,fig.height=4.5,fig.width=5,message=FALSE}
d1 <- dataset %>% 
        group_by(Gender,Test_Type) %>% 
        summarise(mean_time = mean(Time_Sec))

ggplot(d1, aes(x =Gender , y = mean_time,fill=Gender)) +
  geom_bar(stat = "identity",width = 0.8)+
  facet_wrap(~Test_Type)+
  ylab("Mean time")+
  ggtitle("Average time to complete the test by gender and test type")+
  theme_minimal()+
  theme(plot.title = element_text(size=12))

@@

```{r,echo=FALSE,warning=FALSE,message=FALSE}

d2 <- dataset %>% 
        group_by(Rating)%>% 
        summarise(mean_time = mean(Time_Sec))

overall_mean_time<-mean(dataset$Time_Sec)
```

The line chart shown in Figure \@ref(fig:hhhh) is used to visualize the relationship between the degree of enjoyment of music from students and their attention levels. The blue line indicates the average time to complete the test at each rating level, and the brown dash line represents the total average time for accomplishing the test. As we can see from the chart, when the rating is approximately less than 3, the average time for students to complete the test is all greater than the overall average. When the rating is greater than 3, the average time for all students is significantly less than the overall average except for level 4.0. According to the findings in Figure \@ref(fig:hhhh), when students listen to songs they do not like while studying or doing other things that require concentration, their attention level is easily affected.

```{r hhhh, fig.cap="Music favorability and average time to complete the test",echo=FALSE,message=FALSE}
ggplot(d2,aes(x=Rating,y=mean_time))+
  geom_line(color='blue')+
  scale_x_continuous(breaks = seq(1,5,0.5),limits = c(1,5))+
  scale_y_continuous(breaks = seq(0,50,5),limits = c(0,50))+
  geom_hline(yintercept = overall_mean_time,
             color = "darkred",
             linetype = "dashed")+
  geom_text(aes(Rating[1], overall_mean_time , label = "Mean"), vjust= 2)+
  ggtitle("Favorability of music and average time to complete the test")

@@

@@

The analysis in this paper will be done entirely through R[@citeR]. Figure \@ref(fig:randomeffect) below shows the completion time of each student in a different order and test environment. One line represents two Trail Making Tests completed by a student, and the colours help distinguish the test environment. For example, a red line indicates that the student completed the first round of the test with background music and then completed the second round of the test in a quiet environment. Regardless of the experimental environment in which the first round is conducted, Figure \@ref(fig:randomeffect) shows that different people have different initial attention levels, which indicates that there are random effects, predominantly random intercepts. In addition, the slope for each line is different, which imply that random slope also exist. So, the linear mixed model is applicable. It quantified how background music played in the background could impact the students' attention level.

@@

### Random Effects
Three null models with different random effect terms will be established. The models will be compared using the ANOVA function to compare the p-values to see if the model adaptability is improved by adding other items.

The three different random effect terms are as follows:

* `(1| Id)`: Random intercepts and slopes for each Id.  
* `(1 + Test_Type |Id)`: The effect of the background music will vary between each student Id. Random intercepts for test type, random slopes for students influenced by test type.
* `(1 + Test_Type * order | Id)`: Each student Id can have their intercept, random slopes influenced by Test Type and order, and their interaction between Test Type and order.

### Fixed Effects
After finding the best-fitting random effect term, ANOVA will be applied to select the significant variables and compare different models. The model for the study starts with only focused variable, test type. Then, other variables will be included in the model one at a time. From the ANOVA output, if the p-value were smaller than 0.1, the variable would be added to the final model. In the process of determining the best model, ANOVA will be applied and the smaller AIC^[AIC(Akaike information criterion) is a mathematical method for evaluating how well a model fits the data generated. AIC is used to compare different models and determine which one is the best fit for the data[@AIC]] suggests the better model.

@@

Figure \@ref(fig:a1) helps to check the assumption of the variance of the residuals is equal across groups. There seems to be an evenly spread around the central line from the chart(Figure \@ref(fig:a1)) and no patterns evident, which means the assumption of homogeneity of variance being satisfied.

```{r a1, fig.cap="The variance of the residuals is equal across groups",echo=FALSE,fig.height=3,fig.width=5}
model<-lmer(Time_Sec~ 1+Test_Type+order+Rating+Gender+(1|Id),data=dataset,REML=FALSE)

@@

QQ plot(Figure \@ref(fig:a2)) can provide an estimation of where the standardized residuals lie for normal quantiles. Substantial deviation from the provided line indicates that the residuals themselves are not normally distributed. From Figure \@ref(fig:a2), there is some deviation from the expected normal line towards the two-side tails. However, overall, the line looks straight and, therefore, pretty normal and suggests that the assumption is not violated.

```{r a2, fig.cap="The residuals of the model are normally distributed",echo=FALSE,fig.height=4,fig.width=4}
library(lattice)
qqmath(model)
```

Multicollinearity means one independent variable can be linearly related to the others[@multicollinearity]. Variance inflation factor(VIF) is utilized to verify the assumption of no multicollinearity because VIF is a measure of the amount of multicollinearity. The bar chart in Figure \@ref(fig:a3) illustrates that all the independent variables in the model have a VIF value less than 2.5, which means there are low, and even no multicollinearity exists.

```{r a3, fig.cap="multicollinearity",echo=FALSE,fig.height=3,fig.width=6}
library(performance)

@@

## Full Model Result
After finding the best-fit random effect term, the predictor variables will be added to the model one by one. Model 1 in the table only includes the most important variable, Test_Type. The result in the table(Table \@ref(tab:r2)) shows that the coefficient of Test_Type is -2.936 with a 90% confidence level is -8.064 to 2.192,  which illustrates that the average time for completing the Trail Making Test with or without background music is not significantly different between groups. Then, the variable order was added to model 2. The result from Table \@ref(tab:r2) shows that the coefficient for the variable order is -10.65 and the 90% confidence interval is  -14.848 to -6.452, which does not cover value 0, suggesting that the average time to complete the test in order 2 is 10.65 seconds faster than the order 1, holding other variables constant. Meanwhile, for model 3, the interaction between test type and order being considered for testing whether the effect of the order variable depending on the level of test type. The output from model 3 shows that the interaction term is not significant, p-value larger than 0.1 and the 90% confidence interval cover value 0. Furthermore, variable Rating was added to model 4 and showed not significantly related to completing the test. Finally, the same logic applied to model 5, which plus variable Gender and illustrate that the different Gender would not be a factor to influence student's time of accomplishing the test.

In order to find out the best-fit model for the data, ANOVA and AIC were applied to compare models. In Table \@ref(tab:r2), there is an AIC value in each model. The smaller the AIC value, the better the model. From Model 1 to Model 5, their AIC values are 760.54, 742.68, 744.21, 746.02, and 747.68. Among them, the AIC value of Model 2 is the smallest. Therefore, it is deduced that Model 2 should be the best model among the five models. To further prove that model two is the best model among the five, ANOVA is used to compare the five models. Table \@ref(tab:r3) analyzes which model is the best by looking at the p-value. When comparing model 1 and model 2, the p-value is much smaller than 0.01, which shows that model two is significantly better than model one, so model two is the best at this time. When comparing model two and model three, the p-value is 0.497, which is greater than 0.1, so adding predictor variables does not increase the fitness of the model. The same logic applies to the comparison between Model 3 and Model 4 and Model 4 and Model 5. In conclusion, through ANOVA's analysis, the conclusion is that Model 2 is still the best.

```{r, echo=FALSE,warning=FALSE,message=FALSE,comment=NA}
library(stargazer)
m1<-lmer(Time_Sec~ 1+Test_Type+(1|Id),data=dataset,REML=FALSE)

@@

m5<-lmer(Time_Sec~ 1+Test_Type+order++Test_Type*order+Rating+Gender+(1|Id),data=dataset,REML=FALSE)
```

```{r r2 ,results='asis', message = FALSE,echo=FALSE}
stargazer(m1,m2,m3,m4,m5,  header=FALSE, type='latex',
                     title = "Linear Mixed Model Result",
          label = "tab:r2")
```

@@

## Model Assessment Result
Root Mean Square Error(RMSE) is used to evaluate the quality of the model. RMSE stands for the standard deviation of the residuals and it helps to tell how concentrated the data is around the best fit line[@RMSE]. In Table \@ref(tab:r4), the RMSE value of the final model, model 2, is 0.135 which a good sign for the model and illustrates that the model has a good ability to predict the data accurately. The R-square is applied to assess the model as well. R-square is a statistical measure of how close the data are to the fitted regression line[@R-square]. R-square consisted two types, which are marginal R-square and conditional R-square for the linear mixed model. The paper will mainly focused on marginal R-square values, which provides the variance explained by only fixed effect. The marginal R-square for the final model, model 2, shown in Table \@ref(tab:r4) is 0.169, which means the final linear mixed model can explain 16.9% of the variation of the dependent variable.

```{r,include=FALSE}
#RMSE:
performance_rmse(m2,normalized = TRUE)

@@

# Discussion

## Ethics Statement
The experiment conducted in this paper is about learning whether background music will influence students' attention level. The intervention in the study is background music. There is no potential to harm or endanger any participant. Moreover, the designer did not collect any sensitive data. Therefore, no formal ethics approval is required.

@@

### Male are more susceptible to music interference
When comparing the average time to complete the test with and without background music for different genders, the results show that the change in female and transexual people is not apparent. After adding interference factors, the average time to complete the test increases by one second. However, the average time for males to complete the test was 45 seconds before adding the interference factor. After the interference factor was added, the average time to complete the test was 50 seconds. The background music increased the completion time for the male by 5 seconds. Therefore, in all the participants in this experiment, males are more likely to be disturbed by background music, which affects their attention level.

@@

### Each Student’s Initial Attention Level is Different
When checking linear mixed model validation, the resulting plot shows that there exist random intercepts and random slopes, which illustrates that each students' initial attention level is different and fixed effects will vary for each student. In other words, the linear mixed model is suitable for this data and can incorporate student-to-student variability in finishing time and improve the ability to describe how fixed effects relate to outcomes.

### Background Music Does not Significantly Affect the Level of Attention of Students
Although in the descriptive analysis, it is found that in the case of background music, the average time for students to complete the test is longer than that without background music. But in the process of comparing the five models, the results show that test_type is not significant among all the models. This shows that it fails to prove that background music will affect the level of attention of students in a statistical sense.
